Paper notes

### 2019-08-15 paper_notes.Rmd
OK editable

library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)

# Here functions that are used.

@@

# f_val <- function(e_w,ew_ng,M,i_v,S){
#   if (round(abs(e_w-ew_ng), digits=2) < i_v) {
#     U <- 1
#     }else{
#       U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
#     }
#   round(U,digits = 2)
# }

@@

$$
U_{(xj,yj)}   = \beta_xx_j + \beta_yy_j + \epsilon_j
$$

@@

$$
U_e=
\begin{cases}
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
\end{cases}
$$

Where: \par
- $U_e$: Ethnic utility
- $x$: number of similar agents in the neighborhood
- $n$: total number of agents in the neighborhood
- $i_e$: desired ethnic composition

@@

```{r ethnic graph function, include=TRUE, echo=FALSE}

@@

symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Symmetric Single Peaked \n\r (S=1,M=0) ") + theme(plot.title = element_text(hjust = 0.5))
constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Linear + Constant \n\r (S=1,M=1)") + theme(plot.title = element_text(hjust = 0.5))
threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Schelling Threshold \n\r (S=0,M=1) ") + theme(plot.title = element_text(hjust = 0.5))

suppressWarnings(
grid.arrange(symmetric_plot, constant_plot,threshold_plot, ncol= 2,nrow = 2)
)

@@

$$
U_v=
\begin{cases}
1, & \text{if} \ e_w \leq i_v, \\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
\end{cases}
$$

@@

```{r value graph function, include=TRUE, echo=FALSE}

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0

@@

subt_cont <- paste0("desired distance = ",i_v)

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

@@

suppressWarnings(
grid.arrange(symm_val_plot, thres_val_plot, ncol= 2,nrow = 2)
)

@@

```{r ethnic utility individual-run, include=TRUE, echo=FALSE}

@@

i_e = 0.7
M = 1
S = 0
n = 8

@@

>>>>

install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
# Here functions that are used.

@@

@@

$$
U^i_{(ej,yj)}   = \beta_xe_j + \beta_yv_j + \epsilon_j
$$

@@

# Ethnic Utility {-}

$$
U^i_e=
\begin{cases}
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
\\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
\end{cases}
$$

Where: \par
- $U^i_e$: Ethnic utility of agent i
- $x$: number of similar agents in the neighborhood
- $n$: total number of agents in the neighborhood
- $i_e$: desired ethnic composition

@@

```{r ethnic graph function, fig.width=6,fig.height= 8, fig.align="center",  include=TRUE, echo=FALSE}

@@

subt_cont_e <- paste0("Desired proportion i = ",i_e)

symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Linear + Constant (S=1,M=1)",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Schelling Threshold (S=0,M=1)",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

suppressWarnings(
grid.arrange(symmetric_plot, constant_plot,threshold_plot, bottom = "Comparison of the three functions for ethnic utility of a neighborhood j")
)

@@

# Value Utility {-}

$$
U^i_v=
\begin{cases}
1, & \text{if} \ e_w \leq i_v, \\
\\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
\end{cases}
$$

Where: \par
- $U^i_v$: Ethnic utility of agent i
- $\overline{ew}_j$: average ethnic weight in neighborhood \textit{j}
- $ew_i$: ethnic weight of agent \textit{i}
- $i_e$: desired ethnic composition

@@

```{r value graph function, fig.width=5,fig.height= 6, fig.align="center", include=TRUE, echo=FALSE}

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0
# M regulates the right side of the slope, S the left side of the slope

@@

subt_cont_v <- paste0("Ethnic weight i = ",e_w,"; ","Desired distance = ",i_v)

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

@@

suppressWarnings(
grid.arrange(symm_val_plot, thres_val_plot, bottom = "Comparison of the two functions for value utility of a neighborhood j.")
)

@@

```{r ethnic utility individual-run,fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}

@@

i_e = 0.3
M = 1
S = 0
n = 7

@@

#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)

M. <- rep(M,9)
S. <- rep(S,9)
prop_des <- rep(i_e,9)
num_tot <- rep(n,9)
num_sim <- seq(0, 8, by = 1)

report_E <- data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E)

knitr::kable(report_E,align="c") # much better printed visualization
